---
title: "README"
author: "Joey Heffner"
date: "December 12, 2018"
output: 
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.path = "README-"
)
```

# fecScrape

The fecScrape package provides functions to interface with the [OpenFEC API](https://api.open.fec.gov/developers/). OpenFEC API allows you to access funding data on candidates and committees. This package allows users to scrape individual- and aggregated-level donation data, plot these data to examine the timecourse of donation as well as geographic spread of donations, and does some basic summary statistics. 

# Thanks

During this class project, we came across another package which inspired our own code and thoughts on how to develop this package. Please check out the [tidyusafec](https://github.com/stephenholzman/tidyusafec) package, written by Stephen Holzman. 

# Installation 

To finish when the R package is complete. 

# Functions

To Do: Create a naming schematic for the functions such that all functions which interface with the OpenFEC API use the "query_" prefix and all functions which plot data use the "plot_" prefix. 

[x] choose_cand
[x] get_contributions_all
[x] get_itemized_contributions
[x] plot_donations
[x] query_candidate_list
[x] query_openfec
[x] top_cities
[x] top_occupations

# Example: 2018 Senate race between Bato & Cruz

## Step 1: Scrape candidates running in an election of interest. 

For our example, we will focus on the recent 2018 Sentate race in Texas between [Beto O'Rourke](https://betofortexas.com) and [Ted Cruz](https://www.cruz.senate.gov). We chose these this specific election because both Beto and Cruz raised tens of millions of dollars for this election cycle. 

```{r, message = FALSE, warning = FALSE, eval = FALSE}

```